Material Methods

### 2020-04-17 doc/MatMeth.Rmd
more updates and changes

Meiocyte spreads were incubated with antibody protocol.

@@

The master mix was made --

>>>>

Meiocyte spreads were incubated with antibody protocol /  Immunohistochemistry was based on that in Anderson et al. (1999) and Koehler et al. (2002).

@@

Antibodies and slide blocking was performed in 1X antibody dilution buffer (ADB) (normal donkey serum (Jackson ImmnuoResearch), 1X PBS, bovine serum albumin (Sigma), Triton X-100 (Sigma) ).

Each slide was blocked for 30 minutes in ADB incubating with sixty ul of primary antibody master mix (60ul) 
was in ADB and incubated for 48 hours at 37 degrees. The master mix was made (with a primary with polyclonal anti rabbit anti-MLH1 (Calbiochem; diluted 1:50) or anti rabbit anti-DMC1) -- (**mix of DMC1**), anti goat polyclonal antibody to SYCP3, (Abcam; diluted 1:50), and anti-human polyclonal antibody to CREST (Antibodies, Inc; diluted 1:200)

Slides were washed twice in 50ml ADB between primary and secondary antibody incubations.

secondary antibodies master mix was made -- Slides were incubated overnight at 37 degrees in Alexa Fluor 488 donkey anti-rabbit IgG (Invitrgoen, location; diluted to 1:100) and Coumarin AMCA donkey anti-human IgG (Jackson ImmunoResearch; diluted to 1:200).

Alexa Fluor 568 donkey anti-goat (Invitrogen; diluted 1:100) was incubated at 1:100 for 2 hours at 37 degrees. Slides were washed in 1x PBS, dried, and fixed with Prolong Gold Antifade (Invitrogen) for at least 24 hours. Mice with at least 10 cells with good staining were included in our analysis.
